---
title: "Organize Your Projects"
linktitle: "1: Organize"
date: "2020-12-20"
menu:
  year3:
    parent: "Workflow"
type: docs
weight: 1
---

```{r setup, include = FALSE, cache = FALSE}
knitr::opts_chunk$set(error = TRUE, comment = NA, warnings = FALSE, errors = FALSE, messages = FALSE, tidy = FALSE, echo = FALSE)
```

So you have a great idea?! That's awesome. Chances are, this great idea didn't come to you while you were sitting comfortably in your office/research space, ready to calmly write down some ideas and carefully organize things. If you're like me, you have an idea when you're riding your bike, or laying down to watch TV before you go to bed, or when your kids are all having a breakdown and you decide to reorient your research toward to costs and benefits of corporal punishment.

Here, we'll share some things that seem to work for organizing your research ideas and, eventually, your full research projects.

<center>

```{r}
knitr::include_url("https://imccart.github.io/phd-workshop-content/year3/organize.html")
```


<p><a class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/phd-workshop-content/year3/organize.html"><i class="fas fa-external-link-alt"></i> View slides in new window</a> <a class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/phd-workshop-content/year3/organize.pdf" role="button"><i class="far fa-file-pdf"></i> Download PDF of slides</a></p>

</center>
