---
title: "Quickly summarizing your work for the public"
linktitle: "2: Summarizing"
date: "2020-12-20"
menu:
  year4:
    parent: "Will Anyone Read This?"
type: docs
weight: 2
---

```{r setup, include = FALSE, cache = FALSE}
knitr::opts_chunk$set(error = TRUE, comment = NA, warnings = FALSE, errors = FALSE, messages = FALSE, tidy = FALSE, echo = FALSE)
```


You've written a complete paper - yay!! Now pick someone you know outside of academia and imagine they find your paper. Would they care at all? How would you describe your work (briefly and compellingly) to them?

Here, we'll talk about some simple strategies for quickly summarizing your work for a potentially non-academic audience (or at least an audience not specifically in your field). 

<center>

```{r}
knitr::include_url("https://imccart.github.io/phd-workshop-content/year4/summarize.html")
```


<p><a class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/phd-workshop-content/year4/summarize.html"><i class="fas fa-external-link-alt"></i> View slides in new window</a></p>

</center>
