---
title: "Distributing materials for the job market"
linktitle: "3: Distributing materials"
date: "2020-12-20"
menu:
  year4:
    parent: "The Job Market"
type: docs
weight: 1
---

```{r setup, include = FALSE, cache = FALSE}
knitr::opts_chunk$set(error = TRUE, comment = NA, warnings = FALSE, errors = FALSE, messages = FALSE, tidy = FALSE, echo = FALSE)
```


Now that you have all of this content that highlights what a great researcher/teacher/analyst you are, how do you make it accessible to others? Here, we'll make sure everyone has a functional website for their time on the job market.


<center>

```{r}
knitr::include_url("https://imccart.github.io/phd-workshop-content/year4/website.html")
```


<p><a class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/phd-workshop-content/year4/website.html"><i class="fas fa-external-link-alt"></i> View slides in new window</a></p>

</center>


The slides are really just general overview and basic rules to consider. We'll also work through a live example to deploy a site during the workshop.