---
title: "Collecting materials for the job market"
linktitle: "2: Collecting materials"
date: "2020-12-20"
menu:
  year4:
    parent: "The Job Market"
type: docs
weight: 1
---

```{r setup, include = FALSE, cache = FALSE}
knitr::opts_chunk$set(error = TRUE, comment = NA, warnings = FALSE, errors = FALSE, messages = FALSE, tidy = FALSE, echo = FALSE)
```


At this point, you should have a couple of papers under your belt, and it's time to start thinking about other things you need to begin to enter the job market...things like a CV, a syllabus, etc. Here, we'll work through some basic requirements and suggestions for these stand-alone documents.


<center>

```{r}
knitr::include_url("https://imccart.github.io/phd-workshop-content/year4/market-materials.html")
```


<p><a class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/phd-workshop-content/year4/market-materials.html"><i class="fas fa-external-link-alt"></i> View slides in new window</a></p>

</center>

Be sure to check the [resources](/resource/) page to access any Emory-specific templates.
