---
title: "Contribute Positively to Your Office or Department Culture"
linktitle: "5: Culture"
date: "2020-12-20"
menu:
  etiquette:
    parent: "Topics"
type: docs
weight: 5
---

```{r setup, include = FALSE, cache = FALSE}
knitr::opts_chunk$set(error = TRUE, comment = NA, warnings = FALSE, errors = FALSE, messages = FALSE, tidy = FALSE, echo = FALSE)
```

An "office culture" is hard to define. It's basically a system of values, shared assumptions, and group norms. I believe that strong, positive culture can help develop junior faculty, improve teaching, and even improve our research. There's certainly plenty of evidence that a strong culture helps in a traditional office setting.

As academics, we've often developed some odd work habits. Here, we'll talk about some things we should consider and try to improve upon if we want to enjoy our workplace.

<center>

```{r}
knitr::include_url("https://imccart.github.io/phd-workshop-content/etiquette/culture.html")
```

<p><a class="btn btn-primary btn-lg" target="_blank" href="https://imccart.github.io/phd-workshop-content/etiquette/culture.html"><i class="fas fa-external-link-alt"></i> View slides in new window</a></p>

</center>
